---
title: "Memory Analysis"
output: html_notebook
---

# Process a dot file from gperftools and pprof

First, we convert the dot file to json

```{bash}
dot -Tdot_json MemALlA_9_1_all.dot > MemALlA_9_1_all.dot.json
```

Now, we need some libraries
```{r}
library(tidyverse)
library(tidygraph)
library(ggraph)
library(jsonlite)
library(janitor)
library(visNetwork)
```

Turn off an annoying warning (apparenlty due to an R bug that is still not fixed?)
```{r}
options(warnPartialMatchArgs = FALSE)
```

Load in the JSON file and parse it
```{r}
j <- fromJSON("MemALlA_9_1_all.dot.json")
```

The returned R object has `objects` which are the nodes and `edges` that are the connecting lines. We need to convert things to be accepted by `tidygraph`

First of all, we only want nodes that are boxes (e.g. not the legend). We also want an `index` column. We need to figure out what to do with the label. Unfortunately, the label has many forms. Write some somefunctions to deal with it. 

```{r}
last <- function(x) { return( x[length(x)] ) }

nWithPercent <- function(nS) {
  # Capture things like "34.3 (56.3%)" where "of " in front is optional
  r <- str_match(nS, "(?:of )*([0-9.]+) \\(([0-9.]+)%\\)")
  
  list(n=as.numeric(r[2]), p=as.numeric(r[3]))
}


splitUpNodeLabel <- function(label) {
  # Break up by line
  l = str_split(label,"\\\\n|\\\\r", simplify = TRUE)
  
  # The last line should be empty
  # The 2nd to last line should be the total memory
  totalLine = l[length(l)-1]
  totals <- nWithPercent(totalLine)
  totalMem <- totals$n
  totalPerc <- totals$p
  
  # Is there a self?
  selfMem <- NA
  selfPerc <- NA
  whereStart <- 2
  if (str_detect(totalLine, "of ")) {
    selfLine <- l[length(l)-2]
    selfs <- nWithPercent(selfLine)
    selfMem <- selfs$n
    selfPerc <- selfs$p
    whereStart <- 3
  }
  
  # Get the fullPath
  fullPath <- l[length(l) - whereStart]
  
  # Pull out the file and line
  file <- str_split(fullPath, "/", simplify = TRUE) %>% last()
  
  # Merge the rest with spaces
  fcn <- paste(l[1:(length(l)-whereStart-1)], collapse = " ")
  
  tibble(fcn=fcn, file=file, fullPath=fullPath, totalMem=totalMem, totalPerc=totalPerc, selfMem=selfMem, selfPerc=selfPerc)
}
```

Make the nodes dataframe. Here, we use a `purrr` to run our label function that will return a dataframe. `unnest` will turn that into columns. 
```{r}
# See https://stackoverflow.com/a/49985224/819526
nodes <- j$objects %>% 
  clean_names() %>% 
  filter(shape == "box") %>% 
  rename(index = gvid) %>% 
  mutate(f = map(label, splitUpNodeLabel)) %>% 
  unnest(f) %>% 
  mutate(name = fcn) %>% 
  select(index, name, file, fullPath, totalMem, totalPerc, selfMem, selfPerc)
```

```{r}
nodes
```

Let's next fix the edges. 

```{r}
edges <- j$edges %>% clean_names() %>% rename(from = tail, to = head) %>% mutate(mem = as.numeric(label)) %>% select(from, to, mem)
```

Make this into a graph

```{r}
g <- tbl_graph(nodes=nodes, edges=edges)
g
```

Let's find the nodes where the allocations happens (these are at the bottom of the graphs)

```{r}
g %>% 
  filter(node_is_sink()) %>% 
  as_tibble() %>% 
  select(index, name, totalMem, totalPerc) %>% 
  arrange(-totalMem)
```

Let's look at the 2nd highest allocation (index #71). Chosen because it's simple but meaningful. 

```{r}
g %>% 
  mutate(dist = dfs_dist(71, mode="in")) %>% 
  filter(!is.na(dist)) %>% 
  as_tibble() %>% 
  arrange(dist) %>% 
  select(index, name, file, totalMem, dist)
```

Plot the relevant parts

```{r}
g %>% 
  mutate(dist = dfs_dist(71, mode="in")) %>% 
  filter(dist < 5) %>% 
  ggraph(layout="mds" ) + 
    geom_edge_link(
      aes(label=mem),
      label_size=4,
      angle_calc = 'along',
      label_dodge = unit(4, 'mm'),
      arrow = arrow(length = unit(4, "mm")),
      start_cap = circle(6, "mm"),
      end_cap = circle(6, "mm") ) + 
    geom_node_text(
      aes(label = index), size = 7) +
    theme_graph()
```

